---
title: "Congruence compatible"
format: html
editor: visual
execute: 
  echo: false
---

## Definition

Let $S$ be a [numerical semigroup](../Basic-concepts/Numerical-semigroup.qmd) [minimally generated](../Basic-concepts/Minimal-set-of-generators.qmd) by $\{n_1, n_2, \ldots, n_p\}$, an element $s \in S$, $\nabla_s$ the [graph associated](Graph-associated-to-an-element.qmd) to $s$ and $\tau \subseteq \mathbb{N}^p \times \mathbb{N}^p$. It is said that $\tau$ is compatible with $s \in S$ if either $\nabla_s$ is connected or if $R_1, R_2, \ldots, R_t$ are the connected components of $\nabla_s$, then for every $i \in \{1, 2, \ldots, t\}$ it can be chosen $a_i \in R_i$ such that for every $j \in \{1, 2, \ldots, t\}$ with $i \ne j$, there exists $i_1, i_2, \ldots, i_k \in \{1, 2, \ldots, t\}$ fulfilling

-   $i_1 = i, i_k = j$,
-   for every $m \in \{1, 2, \ldots, k-1\}$ either $(a_{i_m}, a_{i_{m+1}}) \in \tau$ or $(a_{i_{m+1}}, a_{i_m}) \in \tau$.

## Examples

$\circ$ Let $S = \langle 5, 7, 11, 13 \rangle$ and $s = 26$. The graph $\nabla_{26}$ is as follows.

```{r librerias, include=FALSE, warning=FALSE}

library(tidyverse)
library(tidygraph)
library(ggraph)
```

```{r grafo ejemplo1, fig.height=3, fig.width=3}
tabla_aristas = data.frame("from" = c( "(3,0,1,0)", "(0,0,0,2)"),
                           "to" = c( "(1,3,0,0)", "(0,0,0,2)"))

ggraph(tabla_aristas, layout = "igraph", algorithm = "kk") + 
  geom_edge_link(width = 1, colour = "lightgray") +
  geom_node_point(size = 6, colour = "lightblue") +
  geom_node_text(aes(label = c("(3,0,1,0)", "(0,0,0,2)", "(1,3,0,0)")), repel = TRUE) +
  coord_fixed() +
  theme_graph()
```

The graph $\nabla_{26}$ is not connected and it has two connected components, $R_1 = \{(1,3,0,0), (3,0,1,0)\}$ and $R_2 = \{(0,0,0,2)\}$. Let $a_{1,1} = (1,3,0,0), a_{1,2} = (3,0,1,0)$ and $a_{2,1} = (0,0,0,2)$, let us see what pairs needs a subset of $\mathbb{N}^4 \times \mathbb{N}^4$ to be compatible with $s = 26$. As $\nabla_{26}$ is not connected, it has to satisfy the second condition.

-   For $i = 1$, we need $a \in R_1, b \in R_2$ such that $(a,b) \in \tau$ or $(b,a) \in \tau$

-   For $i = 2$ we have the same condition as before.

Then, $\tau$ is compatible if has at least one of the following pairs: $(a_{1,1}, a_{2,1}), (a_{2,1}, a_{1,1}), (a_{1,2}, a_{2,1}), (a_{2,1}, a_{1,2})$.

## Examples with GAP

Nowadays, there are no functions in package NumericalSgps related to congruence compatible.

## References
