---
title: "Graph associated to an element by set of factorizations"
format: html
editor: visual
execute: 
  echo: false
---

## Definition

Let $S$ be a [numerical semigroup](../Basic-concepts/Numerical-semigroup.qmd) and $s \in S$. It is defined the graph associated to $s$ as the graph whose vertices are the elements of its [set of factorizations](Set-of-factorizations.qmd) and $a,b$ are related if $a \cdot b \ne 0$, where the dot product multiplies component by component The graph associated to an element $s \in S$ is denoted by $\nabla_s$.

## Examples

$\circ$ Let $S = \langle 5, 12, 13 \rangle$ and $s = 60$. To compute the set of factorizations $\mathbf{Z}(s)$ of $s \in S$, note that $(\alpha, \beta, \gamma) \in \mathbf{Z}(s)$ implies $0 \le \alpha \le 12, 0 \le \beta \le 5$ and $0 \le \gamma \le 4$. From this, it is deduced that

$$
\mathbf{Z}(60) = \{ (12, 0, 0), (0, 5, 0), (7, 1, 1), (2, 2, 2) \}.
$$

The graph associated to $s = 60$ is as follows.

```{r librerias, include=FALSE, warning=FALSE}

library(tidyverse)
library(tidygraph)
library(ggraph)
```

```{r grafo ejemplo1, fig.height=3, fig.width=3}
tabla_aristas = data.frame("from" = c( "(12,0,0)", "(12,0,0)", "(0,5,0)", "(0,5,0)", "(7,1,1)" ),
                           "to" = c( "(7,1,1)", "(2,2,2)", "(7,1,1)", "(2,2,2)", "(2,2,2)" ))

ggraph(tabla_aristas, layout = "igraph", algorithm = "kk") + 
  geom_edge_link(width = 1, colour = "lightgray") +
  geom_node_point(size = 6, colour = "lightblue") +
  geom_node_text(aes(label = c("(12,0,0)", "(0,5,0)", "(7,1,1)", "(2,2,2)")), repel = TRUE) +
  coord_fixed() +
  theme_graph()
```

## Examples with GAP

Nowadays, there are no functions in package NumericalSgps related to graph associated to an element.

## References
