---
title: "Graph associated to an element by minimal generators"
format: html
editor: visual
execute: 
  echo: false
---

<!-- Definición de Num. Sem. -->

## Definition

Let $S$ be a [numerical semigroup](../Basic-concepts/Numerical-semigroup.qmd) [minimally generated](../Basic-concepts/Minimal-set-of-generators.qmd) by $\{n_1, \ldots, n_e\}$, and let $n \in S$. It is defined the graph associated to $n$ in $S$, denoted by $G_n = (V_n, E_n)$, as the graph with vertices

$$
V_n = \{n_i ~ | ~ n - n_i \in S\},
$$

and edges,

$$
E_n = \{\{n_i, n_j\} ~ | ~ n - (n_i + n_j) \in S, i \ne j\}.
$$

It can be proven that the number of connected components of $G_n$ is equal to the number of [R-classes](Factorizations-R-related.qmd) in $\mathbf{Z}(s)$, where $\mathbf{Z}(s)$ denotes the [set of factorizations](Set-of-factorizations.qmd) of $s$ in $S$.

## Examples

$\circ$ Let $S = \langle 6, 7, 11, 15 \rangle$ and $n = 25$. We have $25 - 6 = 19, 25 - 7 = 18, 25 - 11 = 14, 25 - 15 = 10$, where $\{19, 18, 14\} \subseteq S$ and $15 \not \in S$, then $V_{25} = \{6, 7, 11\}$. Now we compute the edges,

$$
25 - (6 + 7) = 12 \in S, \hspace{0.4cm} 25 - (6 + 11) = 8 \not \in S,
$$

$$
25 - (7 + 11) = 7 \in S.
$$

The graph associated to $n = 25$ is as follows:

```{r librerias, include=FALSE, warning=FALSE}

library(tidyverse)
library(tidygraph)
library(ggraph)
```

```{r grafo ejemplo1, fig.height=3, fig.width=5}
tabla_aristas = data.frame("from" = c( "6", "7" ),
                           "to" = c( "7", "11" ))

ggraph(tabla_aristas, layout = "igraph", algorithm = "kk") + 
  geom_edge_link(width = 1, colour = "lightgray") +
  geom_node_point(size = 4, colour = "lightblue") +
  geom_node_text(aes(label = c("6", "7", "11")), repel = TRUE) +
  coord_fixed() +
  theme_graph()
```

```{r}

#graph G {
  #layout = neato
#  overlap = false
#  node [shape = circle, fixedsize = true, width = 0.9]; (6, 7); (7, 11)
 # (6, 7) -> (7, 11);
#}

```

## Examples with GAP

The following example is made with the package NumericalSgps in GAP.

$\diamond$ Let $S = \langle 14, 27, 31, 33, 77 \rangle$, in GAP:

``` gap
gap> S := NumericalSemigroup(14, 27, 31, 33, 77);
<Numerical semigroup with 5 generators>
```

Given a numerical semigroup $S$ and an element $n$ of it, the function `GraphAssociatedToElementInNumericalSemigroup` returns the graph associated to $n$ in $S$.

``` gap
gap> GraphAssociatedToElementInNumericalSemigroup(114,S);
[ [ 14, 27, 31, 33 ],
  [ [ 14, 27 ], [ 14, 31 ], [ 27, 31 ], [ 27, 33 ] ] ]
```

The graph $G_{114}$ is as follows.

```{r}

#graph G {
 # layout = neato
#  overlap = false
 # node [shape = circle, fixedsize = true, width = 0.9]; 14; 27; 31; 33;
#  14 -> 27;
  #14 -> 31;
  #27 -> 31;
  #27 -> 33;
#}

```

## References
