---
title: "Catenary degree of an element"
format: html
engine: markdown
---

## Definition

Let $S$ be a [numerical semigroup](../Basic-concepts/Numerical-semigroup.qmd), let $s \in S$ and let $\mathbf{Z}(s)$ be the [set of factorizations](../Presentations-NS/Set-of-factorizations.qmd) of $s$ in $S$. It is defined the catenary degree of $s$, denoted by $\mathbf{C}(s)$, as the least $N$ such that for any two factorizations $x, y \in \mathbf{Z}(s)$, there is an [N-chain](Chain-of-factorizations.qmd) joining them.

From the catenary degree of an element it is defined the [catenary degree of a numerical semigroup](Catenary-degree-of-a-numerical-semigroup.qmd).

## Examples

$\circ$ Let $S = \langle 6, 13, 17\rangle$ and $s = 85$. The set of factorizations is

$$
\mathbf{Z}(85) = \{(12, 1, 0), (7, 2, 1), (2, 3, 2), (0, 0, 5)\}.
$$

If we compute the distance between each pair, it is obtained the following graph.

```{r librerias, include=FALSE, warning=FALSE}

library(tidyverse)
library(tidygraph)
library(ggraph)
```

```{r grafo ejemplo1, fig.height=5, fig.width=5}
tabla_aristas = data.frame(
  "from" = c( "(12, 1, 0)", "(12, 1, 0)", "(12, 1, 0)",
              "(7, 2, 1)", "(7, 2, 1)",
              "(2, 3, 2)"),
  "to" = c( "(7, 2, 1)", "(2, 3, 2)", "(0, 0, 5)",
            "(2, 3, 2)", "(0, 0, 5)",
            "(0, 0, 5)"),
  "weight" = c(5, 10, 13, 5, 9, 5))


ggraph(tabla_aristas, layout = "igraph", algorithm = "kk") + 
  geom_edge_link(width = 1, colour = "lightgray") +
  geom_edge_hive(aes(label = tabla_aristas[, "weight"]), strength = 0) +
  geom_node_point(size = 5.5, colour = "lightblue") +
  geom_node_text(aes(label = c("(12,1,0)", "(7, 2, 1)", "(2, 3, 2)", "(0, 0, 5)")), repel = TRUE, nudge_y = 0.1) +
  coord_fixed() +
  theme_graph()
```

From this graph, it is deduced that the least $N$ is $N = 5$, concluding that $\mathbf{C}(85) = 5$.

## Examples with GAP

The following example is made with the package NumericalSgps in GAP.

$\diamond$ Let $S = \langle 47, 63, 81, 90 \rangle$, in GAP:

``` gap
gap> S := NumericalSemigroup(47, 63, 81, 90);
<Numerical semigroup with 4 generators>
```

Given the set of factorizations of an element, the functions `CatenaryDegree` and `CatenaryDegreeOfSetOfFactorizations` compute the catenary degree with respect to the given set of factorizations.

``` gap
gap> z := Factorizations(715, S);
[ [ 2, 6, 3, 0 ], [ 2, 2, 5, 1 ], [ 2, 7, 0, 2 ], [ 2, 3, 2, 3 ],
  [ 2, 0, 1, 6 ] ]
gap> CatenaryDegree(z);
4
gap> CatenaryDegree(z) = CatenaryDegreeOfSetOfFactorizations(z);
true
```

If we give a numerical semigroup $S$ and an element $n$ of it in `CatenaryDegree`, then the function returns the catenary degree of $n$ in $S$.

``` gap
gap> CatenaryDegree(715, S);
4
gap> CatenaryDegree(S, 715);
4
```

Moreover, if we give only a numerical semigroup $S$, the function returns the catenary degree of $S$.

``` gap
gap> CatenaryDegree(S);
9
```

## References
