---
title: "Chain of factorizations"
format: html
engine: markdown
---

## Definition

Let $S$ be a [numerical semigroup](../Basic-concepts/Numerical-semigroup.qmd), let $s \in S$ and let $\mathbf{Z}(s)$ be the [set of factorizations](../Presentations-NS/Set-of-factorizations.qmd) of $s$ in $S$. Given $x,y \in \mathbf{Z}(s)$ and a non-negative integer $N$, it is said that $x_1, x_2, \ldots, x_k \in \mathbb{Z}(s)$ is an $N-$chain joining $x$ and $y$ if

-   $x_1 = x$, $x_k = y$,

-   for all $i \in \{1, 2, \ldots, k-1\}$, $d(x_i, x_{i+1}) \le N$, where $d(x_i, x_{i+1})$ denotes the [distance](Distance-factorizations.qmd) between $x_i$ and $x_{i+1}$.

## Examples

$\circ$ Let $S = \langle 5, 12, 16 \rangle$ and $s = 70$. The set of factorizations is

$$
\mathbf{Z}(70) = \{(14, 0, 0), (2, 5, 0), (6, 2, 1), (2, 1, 3)\}.
$$

If we compute the distance between each pair, it is obtained the following graph.

```{r librerias, include=FALSE, warning=FALSE}

library(tidyverse)
library(tidygraph)
library(ggraph)
```

```{r grafo ejemplo1, fig.height=5, fig.width=5}
tabla_aristas = data.frame(
  "from" = c( "(14,0,0)", "(14,0,0)", "(14,0,0)",
              "(2,5,0)", "(2,5,0)",
              "(6,2,1)"),
  "to" = c( "(2,5,0)", "(6,2,1)", "(2,1,3)",
            "(6,2,1)", "(2,1,3)",
            "(2,1,3)"),
  "weight" = c(12, 8, 12, 5, 4, 5))


ggraph(tabla_aristas, layout = "igraph", algorithm = "kk") + 
  geom_edge_link(width = 1, colour = "lightgray") +
  geom_edge_hive(aes(label = tabla_aristas[, "weight"]), strength = 0) +
  geom_node_point(size = 5.5, colour = "lightblue") +
  geom_node_text(aes(label = c("(14,0,0)", "(2,5,0)", "(6,2,1)", "(2,1,3)")), repel = TRUE, nudge_y = 0.1) +
  coord_fixed() +
  theme_graph()
```

Let us consider $x = (2,1,3)$ and $y = (14,0,0)$. We have an $8-$chain, since the sequence $x_1 = x, x_2 = (6,2,1), x_3 = y$ is such that $d(x_1, x_2) = 5$ and $d(x_2, x_3) = 8$. In fact, $N = 8$ is the least $N$ so that for any two factorizations of $s = 70$ there is an $8-$chain. It is said that $N = 8$ is the [catenary degree](Catenary-degree-of-an-element.qmd) of $s = 70$ in $S$.

## Examples with GAP

Nowadays, there are no functions in package NumericalSgps related to $N-$chain of factorizations.

## References
